The Shades of Racism in the Beauty Industry

### 2023-04-19 outputs/paper/paper.qmd
Limitation section

The problem is, beauty products from black owned brands are not making enough to survive in the industry. The lack of representation translates to the business side of the beauty industry as well. There is very limited selection in drugstores and department stores, making it very difficult for the customer to even get access to these products in the first place. It is even more diffult for Black-owned businesses to gain a share of the market. As a result, they cannot get access in order to develop a loyal base of customers. There are no studies done on the needs of people of color, so business owners struggle to validate the need for their brand in the industry. It is harder to build a supportive network of individuals to support a business owner on the entrepreneurial journey. On every step of the way, black womena and women of color face obstacles that threaten their success. It is a system that needs to be addressed on the institutional level, which means that all major institutions need to put systems in place to support these women on every level, media and representation, marketing, research, and business.

@@

>>>>

The problem is, beauty products from black owned brands are not making enough to survive in the industry. The lack of representation translates to the business side of the beauty industry as well. There is very limited selection in drugstores and department stores, making it very difficult for the customer to even get access to these products in the first place. It is even more difficult for Black-owned businesses to gain a share of the market. As a result, they cannot get access in order to develop a loyal base of customers. There are no studies done on the needs of people of color, so business owners struggle to validate the need for their brand in the industry. It is harder to build a supportive network of individuals to support a business owner on the entrepreneurial journey. On every step of the way, black women and women of color face obstacles that threaten their success. It is a system that needs to be addressed on the institutional level, which means that all major institutions need to put systems in place to support these women on every level, media and representation, marketing, research, and business.

@@

There are a few weaknesses and limitations in this paper. Firstly, our analysis only covers representation in fashion culture and the range of products available in the makeup industry. Analysis can and should be done in other areas of the beauty industry, on both the product and service side. Secondly, there are limitations in the calculation of the lightness value. It does not include the various undertones in skin, and difference in makeup products and ingredients needed for people with deeper complexions. It is often the case that while some brands may offer foundation shades that are darker, but that does not mean that those shades are usable. Lack of research on the needs of people of color that often results in foundation shades that are the wrong undertone, too grey, orange, or red. The same goes for the lightness value calculation off of the Vogue covers. Vogue covers are heavily edited, with a team behind them for camera work, lighting, and editing. This could have skewed the depth of the complexion of the deeper skinned models, since according to @fig-all_white, there is a great deal of fluctuation in the skin tone to get an accurate understanding. Next steps would include using the hex code of the models foundation shade to get a more accurate representation of skin tone.
